---
title: "Task 6"
author: "Austin"
date: "9/13/2022"
output: html_document
keepmd: TRUE
editor_options: 
  chunk_output_type: console
---

```{r Loading packages}
library(lubridate)
library(tidyverse)
library(ggplot2)
library(knitr)
library(readr)
library(downloader)
library(dplyr)
library(lubridate)
library(ggrepel)
```

```{r}
dat <- iris
dat
head(dat)
```

```{r}

Largest_width <- dat %>%
  group_by(Species) %>%
  filter(row_number(desc(Petal.Width)) == 1)
Largest_width

Longest_length <- dat %>%
  group_by(Species) %>%
 filter(row_number(desc(Petal.Length)) == 1)
Longest_length
```

```{r}
graph1 <- ggplot(data = dat, mapping = aes(y = Sepal.Width, x = Sepal.Length, color = Species, shape = Species)) +
  geom_point() +
  geom_point(size = 3, shape = 1, color = "black", data = Largest_width) +
  geom_point(size = 3, shape = 1, color = "black", data = Longest_length) +
  geom_text(aes(color = Species, label = "Largest Petal Width"), data = Largest_width, nudge_y = -0.15) +
  geom_text(aes(color = Species, label = "Longest Petal Length"), data = Longest_length, nudge_y = -0.15) +
  labs(y = "Sepal Width (cm)", x = "Sepal Length (cm)", title = "Different Iris Species Have Different Sepal Sizes") +
  theme(legend.position = "bottom")
graph1

```
```

```{r}
ScrabbleData <- tempfile()
download.file("https://media.githubusercontent.com/media/fivethirtyeight/data/master/scrabble-games/scrabble_games.csv",
ScrabbleData, mode = "wb")
ScrabbleDat <- read_csv(ScrabbleData)

ScrabbleAll <- ScrabbleData %>%
  select(date, winnerscore, loserscore) %>%
  pivot_longer(c("winnerscore","loserscore"), names_to = "win-loss", values_to = "score") %>%
  filter(score > 0) %>%
  mutate(year = year(date),
         week = week(date))
         
```

```{r}
avgscrable <- ScrabbleAll %>%
  filter(year == 2005 | year == 2006) %>%
  group_by(year, week) %>%
  summarise(averagescore = mean(score), date = max(date))
avgscrable

firstavg <- avgscrable %>%
  filter(year == "2005")
firstavg

lastavg <- avgscrable %>%
  filter(year == "2006") 
lastavg
```

```{r}
ggplot(data = avgscrable, mapping = aes(x = Date, y = avglength)) +
  geom_point() +
  geom_smooth(data = firstavg, method = 'lm', color="orange") +
  annotate("text", x=as.Date("2005-12-01"), y = 380, label = "Trend Before", color = "orange", size = 3) + geom_smooth(data = lastavg, method = 'lm', color = "blue") +
  annotate("text", x=as.Date("2006-07-15"), y = 380, label = "Trend After", color = "blue", size = 3) + 
  geom_vline(xintercept=as.Date("2006-03-01"), linetype = "dotted") +
  annotate ("text", x = as.Date("2006-03-01"), y = 390, label = "Dictionary\nUpdated", size = 3) +
  labs(y = "Average Score", x = "", title = "Scrabble scores in the age of 'QI' and 'ZA'", subtitle = 'Weekly average scores before and after the addition of around 11,000 words to the Scrabble dictionary', caption = 'Source: FiveThirtyEight') +
  coord_cartesian(ylim = c(355,405), expand = FALSE) +
  scale_x_date(date_breaks = "3 month") +
  limits = as.Date(c('1/6/2005', '1/9/2006')) + 
  theme_bw()
```

