---
title: "R document"
output: 
  html_document:
  keep_md: TRUE
---

```{r}
library(tidyverse)
data(iris)
str(iris)
```
 
```{r}
#Convert the iris data to a tibble called iris_data.
dat <- as_tibble(iris)
```
 
```{r}
# Arrange the iris data by Sepal.Length and display the first ten rows.
Top_ten<- arrange(dat, Sepal.Length)
Top_ten
```
 
 
```{r}
# Select the Species and Petal.Width columns and put them into a new data set called testdat.
testdat <- select(iris, Species, Petal.Width)
testdat
```
 
```{r}
# Create a new table called species_mean that has the mean for each variable for each Species.
species_means <- dat %>%
  group_by(Species) %>%
  summarise(mean(Sepal.Length), mean(Sepal.Width), mean(Petal.Width), mean(Petal.Length))
species_means
```

```{r}
#Create a data frame called iris_min with only the observations with at least 3 for Sepal.Width and not 2.5 for Petal.Width.
Widths <- select(dat, Sepal.Width, Petal.Width)
iris_min <- filter(Widths, Sepal.Width >= 3, Petal.Width != 2.5)
iris_min
```

```{r}
#Create a data frame called iris_size with a column Sepal.Size
iris_size <- dat %>%
  mutate(Sepal.Size = case_when(
    Sepal.Length < 5 ~ "Small",
    Sepal.Length >= 5 & Sepal.Length < 6.5 ~ "Medium",
    Sepal.Length >= 6.5 ~ "Large"))
head(iris_size)
```

```{r}
#Create a data frame called iris_rank which ranks all of the data by Petal.Length, where a ranking of 1 is the largest Petal.Length and order by ranking.
iris_rank <- arrange(dat, desc(Petal.Length))
iris_rank
```
 
```{r}
#Read about the ?summarize_all() function and get a new table with the means and standard deviations for each species.
Mean_std <- dat %>%
  group_by(Species) %>%
  summarise_all(list(Mean=mean, Std_dev = sd)) 
Mean_std
```

#How much pollution is created by Gasoline vehicles compared to Electric and alternative fueled vehicles?

#I had several people reply that gasoline vehicles produce the most pollution most were saying because of the volume rather than the individual impact of a certain vehicle. Others stated that Electric produce the most pollution because of the batteries when they are produced. 

#I asked a friend of mine who is in the diesel and gasoline industry and who has done research on Electric vehicles. He did say that this a possible topic that could be answered in 2 months. He did have some criticism about electric vehicles not having a lot of open research on pollution of Electric vehicles.

 
 
 
 
 
 
 
 
 
 
 
 