---
title: "CaseStudy9"
author: "Austin"
date: "11/2/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(knitr)
library(tidyverse)
library(downloader)
library(corrplot)
library(stringi)
library(stringr)
library(dplyr)
library(ggplot2)
library(haven)
library(readxl)
library(lubridate)
library(readr) 
library(haven)
library(riem)
library(tidyquant)
library(timetk)
library(DT) 
library(dygraphs)

```

```{r}
tickers_today <- tq_get(c("CXW", "F", "GM", "HSY", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT"), get = "stock.prices", from = today()-years(5), to = today())
head(tickers_today)
```
JCP stock was not found so I replaced it with Hershey
```{r}
Graphic1 <- tickers_today %>% 
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date) 
head(Graphic1)
dygraph(Graphic1)
```

```{r}
Graphic2 <- ggplot(data = tickers_today, aes(x = date, y = volume, color = symbol)) +
  geom_line() +
  labs(x = "Date", y = "Volume", title = "Stock volume over time") +
  theme()
Graphic2
```
Overall the dygraph is helpful in to see all the graphs together and is much easier to read compared to the ggplot. The GG plot graphic is too clumped together to be able to understand much of what is going on in the graphic. I thing that using less stocks and deciding a variable to separate the stocks into group with help with reading the graph.
