---
title: "Casestudy 5"
author: "Austin"
date: "9/27/2022"
output: 
  html_document:
  keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r Loading packages}
library(tidyverse)
library(ggplot2)
```

```{r Loading files}
download.file("https://raw.githubusercontent.com/fivethirtyeight/guns-data/master/full_data.csv", "gundata")
dat <- read.csv("gundata")
head(dat)
dat
```

```{r}
agegroups <- dat %>%
  filter(intent != "", age != "") %>%
  mutate(agegroup = 
           case_when(  
             age >= 0 & age <= 14 ~ "under 15",
             age >= 15 & age <= 34 ~ "15-34",
             age >= 35 & age <= 64 ~ "35-64",
             age >= 65 ~ "65+"),
         agegroup = fct_relevel(agegroup,
                                "under 15", "15-34", "35-64", "65+"))
agegroups
```

```{r Age}
Graph1<- ggplot(data = agegroups, aes(x = agegroup, fill = sex)) +
  geom_bar() +
  facet_wrap(~intent, nrow = 2, scales = 'free') +
  scale_fill_manual(values = c("#E7298A", "#0000FF"))+
  ggtitle("Deaths by Age group caused from Guns") +
  theme_bw()
Graph1
```
Not suprising Men have a higher count for all ages for each genre of death most of the deaths are caused from homicides and suicides.
```{r Gender}
Graph2 <- ggplot() +
  geom_density(data = dat, aes(x = age, fill = intent), alpha = .5, position = 'fill', adjust = 1.5) +
  facet_wrap(~sex) +
    scale_fill_manual(values = c("#00FF00","#D95F02","#E7298A", "#0000FF", ))+
  labs(x = "Age", y = "Density",title = "Gun Death Density  by Gender")
Graph2
```
Homicides occur mostly during younger ages under 30, Suicide rate increase as age gets higher for men while woman suicide age peaks in between the 50-70s age range. Undetermined has steady level of density but for men in their late ages spike.
I tried to recolor with out creating a position stack but did not change the colors

```{r Seasons}
seasondat <- dat %>%
  mutate(season = 
            case_when(
            month >= 1 & month <= 2 ~ "Winter",
            month == 12 ~ "Winter",
            month >= 4 & month <= 6 ~ "Spring",
            month >= 5 & month <= 8 ~ "Summer",
            month >= 9 & month <= 11 ~ "Fall",))
seasondat
nonull_seasondat %>%
  filter(season != "")
nonull_seasondat 

Graph3 <- ggplot(data = nonull_seasondat, mapping = aes(x = season, fill = season)) +
  geom_bar() +
  facet_wrap(~sex)+
  labs(x = 'Season', y = 'Deaths', title = 'Deaths by Season')
Graph3

Springdat <- nonull_seasondat %>%
    filter(season == 'spring')

Graph4 <- plot4 <- ggplot(data = Springdat, mapping = aes(x = intent, fill = sex)) +
  geom_bar() +
  facet_wrap(~sex)+
  labs(x = 'Type', y = 'Deaths', title = 'Deaths in the Spring by Type')
Graph4

```
Graph 3 shows the different amount of deaths per season with spring having the most deaths
Graph 4 shows just spring data
