---
title: "Task 5"
author: "Austin"
date: "9/12/2022"
output: 
  html_document:
  keep_md: TRUE
code_folding: 'hide'
editor_options: 
  chunk_output_type: console
---

```{r Packages}
library(tidyverse)
library(downloader)
library(readxl)
```
Comment on the data types. Did they import correctly?
```{r Solodata}
SoloData <- read_csv("solo-artist-followers.csv")
head(SoloData)
SoloData
problems(SoloData)
```
All data imported correctly as chr(characters)


```{r}
BillboardData <- read_csv("billboard-hits.csv")
BillboardData
tail(billboard)
problems(BillboardData)
```
This data has the same variable as the previous dat. This data is missing several of the billboards names and bands I looked at the tail of the data and saw that not all of the data is like this. This means that it is part of the data so it imported correctly

n BillboardData remove all singers who do not have at least 6 times they had a top 100 hit.
```{r}
at_least_six_solo <- BillboardData %>%
  group_by(name) %>%
  filter(n() > 6, band != "")
at_least_six_solo

bestbands <- BillboardData %>%
  group_by(band) %>%
  filter(band %in% at_least_six)
head(at_least_six)

Graph1 <- ggplot(data = at_least_six_solo, aes(x = peak_date, y = peak_rank, color = name, group = name)) +
  geom_point() +
  geom_line() +
  geom_point(data = bestbands, color ="black") +
  geom_line(data = bestbands, color = "black", linetype = "dotted") +
  facet_wrap(~ band, scales = "free") +
  xlab("peak_date") + ylab("peak_rank") +
  theme_bw() 
Graph1
```

```{r}
Climate <- BillboardData <- read_csv("global_sealevel.csv")
problems()

firearms <- read_csv("nics-firearm-background-checks.csv")
problems()

natality <- read_csv("natality - natality.csv")
```

