---
title: "Case study 4"
author: "Austin"
date: "9/19/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(nycflights13)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(readr)
library(tidyverse)
library(knitr)
library(downloader)
library(dplyr)
```

```{r}
?nycflights13
dat <- nycflights13::flights
head(dat)
```

```{r delays delta}
delay <- dat %>%
  filter(carrier == "DL", arr_delay > 0) %>%
  group_by(origin) %>%
  count()
delay

delta <- ggplot(data=delay, mapping=aes(origin, n, fill=origin)) +
  geom_bar(stat="identity", position="dodge") +
  labs(y = "Number of Delays",
       x = "Airport of Origin",
       title = "Number of Flights Per Airport that are delayed") +
  theme(legend.position = "none")
delta
```
2. Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?
The airport with the fewest delays would be EWR or also known as Newark. Flying delta from this airport will minimize the chance of delay

```{r worst arrival}
worst_arrival <- flights %>%
  group_by(dest) %>%
  summarise(avg_delaytime = mean(arr_delay, na.rm = TRUE)) %>%
  filter(avg_delaytime > 15)
worst_arrival

worst <- ggplot(data=worst_arrival, mapping=aes(dest, avg_delaytime, color=dest)) +
  geom_point() +
  labs(y = "Average arrival Time",
       x = "Destination Airport",
       title = "Worst airport arrival times(>15mins)") +
  theme(legend.position = "none")
worst
```
3. Which destination airport is the worst airport for arrival time?
From my observaion I have found that CAE or also known as Columbia metropolitan airport has the worst arrival times of any airport.


